Software Ticket Quality

### 2017-12-05 proposal/mprop.tex
Add paper on sentiment analysis

\textbf{Effects of process maturity on quality, cycle time and effort in software product development}\cite{harter2000effects}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The research tries to investigate the relationship between process maturity, quality, cycle time and effort in software projects. The authors are mainly trying to prove/
  reject a couple of hypotheses: higher levels of process maturity lead to higher product quality in software projects, higher levels of process maturity are associated 
  with increased cycle time in software products, higher product quality is associated with lower cycle time, higher levels of process maturity lead to increased 
  development efforts in the project and higher product quality is associated with lower development effort.
  \item \textbf{What was the method?}
  In order to test their hypotheses, the authors examined data coming from 30 projects belonging to the systems integration division from a large IT company. The process 
  improvement data was collected via external divisions and by government agencies to provide independent assessments of the firm’s software development processes. Then, 
  they analyzed a couple of key variables and see how they interact: process maturity, product quality, cycle time, development effort, product size, domain/data/decision 
  complexity and requirements ambiguity.
  \item \textbf{What did they learn?}
  They learned that the main features they inspected are additively separable and linear. Moreover, they found out that higher levels of process maturity are associated 
  with significantly higher quality, but also with increased cycle times and development efforts. On the other hand, the reductions in cycle time and effort resulting from 
  improved quality outweigh the marginal increases from achieving more process maturity.
  \item \textbf{Relevance to our work}:
  It can aid our research through better understanding of how various factors can influence the software development processes, thus giving more value to our own research 
  (i.e. being able to automatically determine issue quality could improve better issue writing guidelines/better rules to be enforced, thus reduced triaging and 
  development costs). 
\end{itemize}

\subsection{Sentiment Analysis}

\textbf{Thumbs Up or Thumbs Down}\cite{turney2002thumbs}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to detect the overall sentiment transmitted
    through reviews of various types.
  \item \textbf{What was the method?}
    The author created an unsupervised machine learning algorithm that was 
    evaluated on more than 400 reviews on Epinions on various kinds of markets 
    (e.g.\ automobiles, movie). The algorithm implementation was divided 
    into three steps:
      \begin{itemize}
        \item extract phrases containing adjectives or adverbs;
        \item estimate the semantic orientation of the phrases;
        \item classify the review as recommended or not recommended based on
          the semantic orientation calculated at previous step.
      \end{itemize}
  \item \textbf{What did they learn?}
    One thing the author learned that different categories will yield different 
    results. For example, the automobile section on Epinions ranked much higher, 
    84\%, compared to movie reviews, which had an accuracy of 65.83\%. Moreover, 
    most pitfalls of the algorithm could be attributed to multiple factors, such 
    as not using a supervised learning system or limitations of PMI-IR.
  \item \textbf{Relevance to our work}: the method can be applied for extracting
    sentiments from the tickets (description and comments) we will use 
    in our own research.
\end{itemize}

>>>>

As we want to analyze comments as well and how they influence the quality of a ticket, we
need to investigate what state-of-the-art tools are available to perform sentiment analysis.
One paper that tried to detect the overall sentiment transmitted through reviews of various 
types is the research performed by \citet{turney2002thumbs}. The author created an unsupervised
machine learning algorithm that was evaluated on more than 400 reviews on Epinions on various
kins of markets. The algorithm implementation was divided into three steps:
  \begin{itemize}
    \item extract phrases containing adjectives or adverbs;
    \item estimate the semantic orientation of the phrases;
    \item classify the review as recommended or not recommended based on
      the semantic orientation calculated at previous step.
  \end{itemize}
The author learned that different categories will yield different results, such as the
automobile section on Epinions ranked much higher, 84\%, compared to movie reviews, which
had an accuracy of 65.83\%. Moreover, most pitfalls of the algorithm could be attributed
to multiple factors, such as not using a supervised learning system or limitations of 
PMI-IR.

However, the work of \citet{turney2002thumbs} looks only at sentiment analysis without
examining the context.
